Desert Ant Behaviour: Modelling desert ants with a focus on movement and navigation

### 2011-12-11 doc/paper.tex
working on doc

\title{Simulate Desert Ant Behaviour}
\author{Georg Wiedebach, Wolf Vollprecht}
\date{date}

@@

\section*{\centerline{Abstract}}
This paper is the final result of the course {\sc Modeling Social Systems with MATLAB} which aimed to offer an insight into the MATLAB programming language and to use said language to model social systems with various different approaches. The timeframe of the course is one semester. \\
In this paper we will try to show how to replicate the behaviourr of desert ants in a MATLAB simulation. Furthermore we will discuss our results and compare them to experimental results obtained by biologists.

>>>>

\title{Desert Ant Behaviour: Modelling desert ants with a focus on movement and navigation}
\author{Georg Wiedebach, Wolf Vollprecht}
\date{\today}

@@

\begin{abstract}
This paper is the final result of the course {\sc Modeling Social Systems with MATLAB} which aimed to offer an insight into the MATLAB programming language and to use said language to model social systems with various different approaches. The timeframe of the course is one semester. \\
In this paper we will try to show how to replicate the behaviour of desert ants in a MATLAB simulation. Furthermore we will discuss our results and compare them to experimental results obtained by biologists.
\end{abstract}
